%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Dr. Diego}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{de Pablos}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.37\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{London, UK}\\
	\icon{Phone}{12}{+ 44 (0) 7784 78 69 81}\\
	\icon{At}{12}{\href{mailto:d.depablosaguero@gmail.com}{d.depablosaguero@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.2\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{https://github.com/D-DePablos}{D-DePablos}}\\
    \icon{LinkedinSquare}{12}{\href{https://www.linkedin.com/in/diego-de-pablos-545a84220/}{Diego de Pablos}}\\
    \icon{NewspaperO}{12}{\href{https://www.researchgate.net/profile/Diego_De_Pablos2/research}{Published Papers}}
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
\entry
		{2022 -- 2023\\\footnotesize{Ongoing}}
		{Fullstack Software Engineer}
		{Urban Jungle}
		{
  - Contributed meaningfully to the engineering team by taking ownership of an external party implementation to provide our car insurance prices for more customers.\\
  - Currently Exploring DevOps through developer enablement, CICD speed-ups, Kubernetes exploitation, and observability work.\\
  - Doubled speed of CICD pipelines to enable faster release rate.\\
  \texttt{Python}\slashsep\texttt{Typescript}\slashsep\texttt{Docker}\slashsep\texttt{Linux}\slashsep\texttt{Mentoring}}
	\entry
		{2022\\\footnotesize{May to September}}
		{Developer Intern}
		{Nethermind}
		{
  - Developed open source blockchain-adjacent applications as part of diverse teams. \\
  - Mentored new joiners on team practices and team members on DevOps technologies. \\
  - Helped document software for more user-friendly resources. \\
  - Contributed to the first release of the Juno StarkNet client (\href{https://gojuno.xyz}{https://gojuno.xyz}).\\
  - Collaborated with other teams to improve development processes.\\\texttt{Github}\slashsep\texttt{Github Actions}\slashsep\texttt{Docusaurus}\slashsep\texttt{Golang}\slashsep\texttt{AWS}\slashsep\texttt{Terraform}\slashsep\texttt{Docker}\slashsep\texttt{TDD}\slashsep\texttt{Pair Programming}}
	\entry
		{2018 -- 2022\\\footnotesize{Seasonal}}
		{Python Mentor}
		{UCL (MSSL)}
		{
  - Created and delivered resources to teach at several MSSL Work Experience events.\\
  - Collaborated with students in programming tasks.\\
  - Presented what being a solar physics researcher looked like on the numerical side.
  \\ \texttt{Python}\slashsep\texttt{Jupyter Notebook}\slashsep\texttt{Public Speaking}\slashsep\texttt{Linux}\slashsep\texttt{Mentoring}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2018 -- 2022}
		{Ph.D in Heliospheric Physics}
		{University College London}
		{Studied the origin of the Solar Wind through a signal analysis algorithm programmed in Python that was created during the project. Collaborated internationally and coordinated several papers to successful publishing.}
	\entry
		{2015 -- 2018}
		{BSc. Environmental Physics}
		{University of Reading}
		{Achieved First class honors in a degree that combined meterology and classical physics. Completed a study of variability of the Earth's radiation belts using publicly available spacecraft data.}
\end{entrylist}

\cvsect{Extracurricular}

\begin{entrylist}
	\entry
		{2022}
		{StarkNet Hackathon}
		{Remote}
		{Won first prize with the most creative DeFi application that allowed for sustainable fixed rate yields.\\ \texttt{React}\slashsep\texttt{NPM}\slashsep\texttt{Cairo} \slashsep\texttt{Python}}
	\entry
		{2018}
		{Hex Hackathon}
		{Eindhoven}
		{Won one of the track challenges, posed by Bloomberg, on peer-to-peer philanthropy.\\ \texttt{JavaScript}\slashsep\texttt{HTML}\slashsep\texttt{CSS} \slashsep\texttt{Public Speaking}}
  \entry
		{2017}
		{UROP Summer Internship}
		{University of Reading}
		{Investigated whether measurements taken from cars were useful for weather forecasting. Findings were presented as part of a presentation and poster competition, and shared with the UK Met Office. \\\texttt{Matlab}\slashsep\texttt{R Studio}\slashsep\texttt{Statistics}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - fluent\\
	\textbf{Spanish} - native\\
	\textbf{French} - elementary
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Interests}
 
    Blockchain Technology\\
    Programming and tech trends \\
    Travelling
    
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Other Skills}

    \textbf{Crypto knowledge:} DeFi, OP/ZK Rollups, Ethereum Improvement Proposals.
    \textbf{Other:} Version Control, Research Methods, Project Management, Academic Writing.
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}

